A Decision Procedure for (Co)datatypes in SMT Solvers

### 2014-12-02 tex/codatadp.tex
more stuff

@@

* monomorphic (or many-sorted) first-order logic
* Signature: $\Sigma = (\mathcal{T}, \mathcal{F})$

@@

We assume a signature $\Sigma = (\mathcal{T}, \mathcal{F})$.

Furthermore, a partition of the types:
  $\mathcal{T} = \mathcal{I} \uplus \mathcal{C} \uplus \mathcal{N}$
with
  * $\mathcal{D}$: datatypes
  * $\mathcal{C}$: codatatypes
  * $\mathcal{N}$: non-(co)datatypes

And a partition of the functions:
  * $\mathcal{C}$

for each datatype or codatatype $\delta$:
  *

In practice, e.g. in an SMT problem, we'd have:
  * declaration of uninterpreted types (in any order)
  * specification of mutual groups of (co)datatypes, in a correct order

>>>>

%\newcommand\Types{\mathcal{T}}
\newcommand\Types{\mathcal{Y}}
\newcommand\Funcs{\mathcal{F}}

\newcommand\Data{\Types_{\mathrm{dt}}}
\newcommand\Codata{\Types_{\mathrm{codt}}}
\newcommand\Nondata{\Types_{\mathrm{other}}}

\newcommand\Ctr{\Funcs_{\mathrm{ctr}}}
\newcommand\Sel{\Funcs_{\mathrm{sel}}}
%\newcommand\Plainfuncs{\Funcs_{\mathrm{other}}}

@@

* monomorphic (or many-sorted) first-order logic
* Signature: $\Sigma = (\Types, \Funcs)$

@@

We assume a signature $\Sigma = (\Types, \Funcs)$.

Furthermore, a partition of the types:
  $\Types = \Data \uplus \Codata \uplus \Nondata$
with
  * $\Data$: datatypes
  * $\Codata$: codatatypes
  * $\Nondata$: non-(co)datatypes

And a partition of the functions:
  $\Funcs = \Ctr \uplus \Sel$
with
  * $\Ctr$: constructors
  * $\Sel$: selectors

(Do not need to consider other function symbols, because they would be
abstracted away as variables in the context of theory combination.)

In practice, e.g. in an SMT problem, we'd have:
  * declaration of uninterpreted types (in any order)
  * list of specifications of mutually (co)recursive groups of (co)datatypes
